T-reX: Quantifying waste and material footprints in current and future Life Cycle Assessment (LCA) databases

### 2024-04-10 latex_files/introduction.tex
accept LL changes

Though steadily emerging~\citep{laurenti2016wastefootprint,demirer2019wastefootprint,guillotreau2023wastefootprint}, the `Waste Footprint' (WF) metric, in contrast, has yet to enjoy such noble recognition for its attempts to measure and classify the waste generated by human activities. While it seems obvious that reducing life cycle waste is critical to the development of the circular economy~\citep{towa2020wastefootprint,ellenmacarthur2015ce}, the WF remains largely overlooked---especially in LCA models where waste itself is seldom apportioned any inherent environmental significance aside from the emissions related to its treatment~\citep{laurenti2023wastefootprint}.
Such neglect strikes the authors as unjustified, given that it has been repeatedly demonstrated that WFs have a strong association with environmental damage~\citep{laurenti2023wastefootprint,doka2024publications, ridoutt2010wasteimpacts,jaio2013wasteabsorbtionfootprint}. Additionally, it has been shown that the most vulnerable communities suffer disproportionately from the social and ecological impacts created by wasteful behaviours and sub-standard end-of-life treatment ~\citep{pellow2023envjusticewaste,akese2018envjustice}.

>>>>

Though steadily emerging~\citep{laurenti2016wastefootprint,demirer2019wastefootprint,guillotreau2023wastefootprint}, the incipient `Waste Footprint' (WF) metric, in contrast, has yet to enjoy such noble recognition for its attempts to measure and classify the waste generated by human activities. While it seems obvious that reducing life cycle waste is critical to the development of the circular economy~\citep{towa2020wastefootprint,ellenmacarthur2015ce}, the WF remains largely overlooked---especially in LCA models where waste itself is seldom apportioned any inherent environmental significance aside from the emissions related to its treatment~\citep{laurenti2023wastefootprint}.
Such ignominious neglect strikes the authors as unjustified, given that it has been repeatedly demonstrated that WFs have a strong association with environmental damage~\citep{laurenti2023wastefootprint,doka2024publications, ridoutt2010wasteimpacts,jaio2013wasteabsorbtionfootprint}. Additionally, it has been shown that the most vulnerable communities suffer disproportionately from the social and ecological impacts created by wasteful behaviours and sub-standard end-of-life treatment~\citep{pellow2023envjusticewaste,akese2018envjustice}.

### 2024-04-10 latex_files/main.tex
accept LL changes

    \begin{abstract}
        % \cbox{Abstract word count: 150, Limit: 150}
        A fundamental principle of ‘circular economy’ is to minimise material consumption and waste generation. Thus, identifying and quantifying waste and material flows is critical. Life Cycle Assessment (LCA) is a powerful method for this, given its capacity to pinpoint hotspots of environmental impact throughout an activity’s life cycle, where the implementation of circular principles could be most effective.

@@

T-reX elucidates the complex relationships between material demand, waste generation, and environmental impacts. This instrument enables detailed exploration of `footprints' and life cycle inventories---modelled externalities of human activities---and examines their connections to supply chain risks and potential environmental damage. T-reX is a step towards a better understanding of these interconnections for the practical realization of `sustainability' and the `circular economy'.

>>>>

    \begin{abstract}
        % \cbox{Abstract word count: 150, Limit: 150}
        The quintessential principle of the ‘circular economy’ is to minimise material consumption and waste generation. Thus, identifying and quantifying waste and material flows is critical. Life Cycle Assessment (LCA) is a powerful method for this, given its capacity to pinpoint hotspots of environmental impact throughout an activity’s life cycle, where the implementation of circular principles could be most effective.

@@

T-reX elucidates the complex relationships between material demand, waste generation, and environmental impacts. This instrument enables detailed exploration of `footprints' and life cycle inventories---modelled externalities of human activities---and examines their connections to supply chain risks and potential environmental damage. T-reX is a step towards a better understanding of these interconnections for the practical realisation of `sustainability' and the `circular economy'.
